Simulation

### 2024-06-26 Bootstrap.Rmd
Mardi soir

```{r}
for (point in 1:n) {
  random_points$x
}
```

```{r}
boot()
```

>>>>

```{r}
# Draft
for (point in 1:n) {
  random_points$x
}
```

```{r}
sum((random_points$x/random_points$y)/pi)
```

```{r}
rho <- function(df, indice){
  d <- df[indice,] # to enable boot
  return(sum((d$x/d$y)/pi))
}
```

```{r}
res_boot <- boot(data=random_points, statistic=rho, R=10)
res_boot
```

```{r}
boot.ci(res_boot, type = "norm")
```

```{r}
boot.ci(res_boot, type = "basic")
# Warning in norm.inter(t, (1 + c(conf, -conf))/2) :
#  extreme order statistics used as endpoints
```

```{r}
# boot.ci(res_boot, type = "stud") 
# Error in ci.out[[4L]] : subscript out of bounds
```

```{r}
boot.ci(res_boot, type = "perc") 
# Error in ci.out[[4L]] : subscript out of bounds
```

```{r}
boot.ci(res_boot, type = "bca") 
# Error in bca.ci(boot.out, conf, index[1L], L = L, t = t.o, t0 = t0.o,  : 
#  estimated adjustment 'a' is NA
```

### 2024-06-26 Draft.Rmd
Mardi soir

>>>>

# Draft for Trees_circle

```{r}
trees_in <- data.frame(useless = rep(0,30942))
col_names <- c()
for (point in 1:n) {
  new_col <- paste("point", point, sep = "")
  a <- random_points[point,]$x
  b <- random_points[point,]$y
  val <- is_point_in_circle(a, b, trees$x, trees$y, 100)*point
  # val <- is_point_in_circle(round(a, digits = 0), round(b, digits = 0), trees$x, trees$y, 100) #*point
  # if (val != 0){
  #  trees$Is_in_circle <- append(trees$Is_in_circle, val[val != 0])
  # }
  trees_in <- trees_in %>% add_column(new_col = val)
  col_names <- append(col_names, new_col)
}
# unique(trees$Is_in_circle)
trees_in[1] <- NULL
colnames(trees_in) <- col_names
```

### 2024-06-26 Simulation1.Rmd
Mercredi midi
Mardi soir

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/artificial_forest_round.xls")
```

@@

```{r}
# True values
cat("Il y a au total", length(trees$x), "arbres et un volume total de", sum(trees$v), "m^3 \n", "Soit un volume moyen de", mean(trees$v), "m^3 \n", "Le diamètre moyen à hauteur de poitrine est de", mean(trees$d130), "cm")
```

@@

```{r}
trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
```

>>>>

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

@@

```{r}
# True values
cat("Il y a au total", length(trees$x), "arbres et un volume total de", sum(trees$v), "m^3 \nSoit un volume moyen de", mean(trees$v), "m^3 \nLe diamètre moyen à hauteur de poitrine est de", mean(trees$d130), "cm")
```

@@

```{r}
trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 2)
```
